### 2025-08-05 03-post-process/output-plots.Rmd
Include code repo DOI in supplement A and README

---
title: '<span style="font-variant: small-caps;"><b><big>Supplement B</big></b></span>'
subtitle: "<small>_A state-space model to quantify density dependence, demographic heterogeneity, and spatial synchrony in Grande Ronde Basin Chinook salmon populations_</small>"
author: |
  | <small>**Authors**: B.A. Staton <a href="https://orcid.org/0000-0002-2342-3482"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, P.P. Gibson <a href="https://orcid.org/0000-0002-9751-7895"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, M. Liermann <a href="https://orcid.org/0009-0004-5019-1471"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, C. Justice <a href="https://orcid.org/0000-0003-0663-5536"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, M.J. Kaylor <a href="https://orcid.org/0000-0001-5331-9830"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, R. Sharma <a href="https://orcid.org/0000-0002-3818-9393"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, and S.M. White <a href="https://orcid.org/0000-0003-4918-6865"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a></small>
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: true
params:
  scenario:
    label: "Scenario"
    value: "final_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_parr_recruitment:
    label: "Include Parr Recruitment Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_processes:
    label: "Include Misc. Processes Output?"
    value: TRUE
  include_composite_rates:
    label: "Include Composite Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_residual_diags:
    label: "Include Residual Diagnostic Output?"
    value: TRUE
  include_pp_check:
    label: "Include Posterior Predictive Check Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_known:
     label: "Include Non-Stochastic Quantities?"
     value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
  include_waic:
    labels: "Include WAIC Output"
    value: FALSE
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: '<span style="font-variant: small-caps;"><b><big>Supplement B</big></b></span>'
subtitle: "<small>_A state-space model to quantify density dependence, demographic heterogeneity, and spatial synchrony in Grande Ronde Basin Chinook salmon populations_</small>"
author: |
  | <small>**Authors**: B.A. Staton <a href="https://orcid.org/0000-0002-2342-3482"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, P.P. Gibson <a href="https://orcid.org/0000-0002-9751-7895"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, M. Liermann <a href="https://orcid.org/0009-0004-5019-1471"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, C. Justice <a href="https://orcid.org/0000-0003-0663-5536"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, M.J. Kaylor <a href="https://orcid.org/0000-0001-5331-9830"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, R. Sharma <a href="https://orcid.org/0000-0002-3818-9393"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, and S.M. White <a href="https://orcid.org/0000-0003-4918-6865"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a></small>
  | [![ArticleDOI](https://img.shields.io/badge/Article-10.1016/j.ecolmodel.2025.111289-blue?logo=doi&logoColor=f5f5f5)](https://www.doi.org/10.1016/j.ecolmodel.2025.111289)    
  | [![CodeDOI](https://img.shields.io/badge/Code%20Archive-10.5281/zenodo.16748911-blue?logo=github&logoColor=f5f5f5)](https://doi.org/10.5281/zenodo.16748911)  
  | [![CodeDOI](https://img.shields.io/badge/Data%20Archive-PLACEHOLDER-blue?logo=github&logoColor=f5f5f5)](https://doi.org/PLACEHOLDER)  
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: true
params:
  scenario:
    label: "Scenario"
    value: "final_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_parr_recruitment:
    label: "Include Parr Recruitment Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_processes:
    label: "Include Misc. Processes Output?"
    value: TRUE
  include_composite_rates:
    label: "Include Composite Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_residual_diags:
    label: "Include Residual Diagnostic Output?"
    value: TRUE
  include_pp_check:
    label: "Include Posterior Predictive Check Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_known:
     label: "Include Non-Stochastic Quantities?"
     value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
  include_waic:
    labels: "Include WAIC Output"
    value: FALSE
editor_options: 
  chunk_output_type: console
---

### 2025-08-05 README.rmd
Include code repo DOI in supplement A and README

[![ArticleDOI](https://img.shields.io/badge/Article-10.1016/j.ecolmodel.2025.111289-blue?logo=doi&logoColor=f5f5f5)](https://www.doi.org/10.1016/j.ecolmodel.2025.111289)  
[![GitHub Code Repo Archive DOI](https://img.shields.io/badge/GitHub%20Code%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()  
[![GitHub Data Repo Archive DOI](https://img.shields.io/badge/GitHub%20Data%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()

>>>>

[![ArticleDOI](https://img.shields.io/badge/Article-10.1016/j.ecolmodel.2025.111289-blue?logo=doi&logoColor=f5f5f5)](https://www.doi.org/10.1016/j.ecolmodel.2025.111289)  
[![GitHub Code Repo Archive DOI](https://img.shields.io/badge/GitHub%20Code%20Repo%20Archive-10.5281/zenodo.16748911-blue?logo=github)](https://doi.org/10.5281/zenodo.16748911)  
[![GitHub Data Repo Archive DOI](https://img.shields.io/badge/GitHub%20Data%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()
